Understanding domestic abuse

### 2019-07-23 JeS_fields.tex
Impact summarry Tim

Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse. We aim to do so by expanding the knowledge of other stakeholders, including the police, charities, and the government.

>>>>

In 2018, there were X thousand victims of domestic abuse in England and Wales alone. Domestic abuse has a terrible impact upon victims in a variety of ways, and ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support. However, the effects of domestic abuse are multi-faceted and far reaching. Such abuse often touches the lives of those far beyond the initial victim, such as children, family, neighbours, friends, and colleagues.

This research uses a variety of existing data sets, to help us better understand patterns of domestic abuse. The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents such as domestic homicide. We will engage with a number of stakeholders, and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.

Many of our primary partners are within the police force. The research will help them to identify individuals who are most at risk of being victims of domestic abuse, and improve risk assessment models to identify situations which could escalate into serious acts of violence. It will also enable the identification of likely triggers for the onset, or worsening of ongoing abuse allowing police to better direct resources and design risk assessment frameworks. The potential triggers that we will investigate include high profile events such as sporting tournaments, and economic shocks, such as changes to the structure of benefit payments. Not only will this help the police, but it will also help policy makers estimate the likely impacts of policy change.

rates of gambling and alcohol spending in the local community, financial wellbeing, and

Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support. However, domestic abuse is multi-faceted and affects the lives of many individuals who  We aim to do so by working together other stakeholders, including the police, charities, and the government.
